---
title: "hw12"
author: "張瑜君"
date: "2019年5月20日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##checkpoint_1_lubridate：

DS4B 101-R: R FOR BUSINESS ANALYSIS

TIME-BASED MATH 
```{r}
library(tidyverse)
library(lubridate)
library(tidyquant)

bike_orderlines_tbl <- read_rds("data_wrangled_student/bike_orderlines.rds")

glimpse(bike_orderlines_tbl)
```


#1.Date & Lubridate Basics

#1-1.Character vs Date/Datetime
```{r}
order_date_tbl <- bike_orderlines_tbl %>%
  select(order_date)

order_date_tbl %>%
  pull(order_date) %>%
  class()
```


#1-2.Date Classes
```{r}
order_date_tbl %>%
  mutate(order_date_chr = as.character(order_date)) %>%
  mutate(order_date_chr2 = order_date_chr %>% str_c(" 00:00:00")) %>%
  
  mutate(order_date_date = order_date_chr %>% ymd()) %>%
  mutate(order_date_dttm = order_date_chr2 %>% ymd_hms())
```


#1-3.Lubridate Functions

#Conversion
```{r}
"06/01/18" %>% mdy() %>% class()

"06/01/18 12:30:15" %>% mdy_hms() %>% class()

"January 1, 1985" %>% mdy()
```


#Extractor
```{r}
"2011-01-01" %>% ymd() %>% year()

"2011-01-01" %>% ymd() %>% month(label = TRUE, abbr = FALSE) 

"2011-01-01" %>% ymd() %>% wday(label = TRUE, abbr = FALSE)

"2011-01-01" %>% ymd() %>% day()
```


#Helpers
```{r}
now()

today()
```


#Periods & Durations - Add/subract time to/from a date
```{r}
today() + days(12)

today() + ddays(12)

today() + years(4)

today() + dyears(4)
```


#Intervals - Calculate time-based distance
```{r}
i <- interval(today(), today() + ddays(12)) 

i / ddays(1) # interval / ddays = how many days in interval

i / dminutes(1) # interval / dminutes = how many minutes in the interval

order_date_tbl %>%
  mutate(today = today()) %>%
  mutate(diff_days = interval(order_date, today) / ddays(1))
```


#2.Time-Based Data Grouping
```{r}
bike_sales_y_tbl <- bike_orderlines_tbl %>%
  select(order_date, total_price) %>%
  mutate(order_date = ymd(order_date)) %>%
  mutate(year = year(order_date)) %>%
  group_by(year) %>%
  summarize(sales = sum(total_price)) %>%
  ungroup()

bike_sales_y_tbl

bike_sales_m_tbl <- bike_orderlines_tbl %>%
  select(order_date, total_price) %>%
  mutate(order_date = ymd(order_date)) %>%
  mutate(
    year  = year(order_date),
    month = month(order_date, label = TRUE, abbr = TRUE)
  ) %>%
  group_by(year, month) %>%
  summarize(sales = sum(total_price)) %>%
  ungroup()

bike_sales_m_tbl
```


#Floor Date
```{r}
bike_orderlines_tbl %>%
  select(order_date, total_price) %>%
  mutate(order_date = ymd(order_date)) %>%
  mutate(year_month = floor_date(order_date, unit = "month")) %>%
  group_by(year_month) %>%
  summarize(sales = sum(total_price))
```


#3.Measuring Change

#3-1.Difference from most recent observation
```{r}
bike_sales_y_tbl %>%
  mutate(sales_lag_1 = lag(sales, n = 1)) %>%
  mutate(sales_lag_1 = case_when(
    is.na(sales_lag_1) ~ sales,
    TRUE ~ sales_lag_1
  )) %>%
  mutate(diff_1 = sales - sales_lag_1) %>%
  mutate(pct_diff_1 = diff_1 / sales_lag_1) %>%
  mutate(pct_diff_1_chr = scales::percent(pct_diff_1))
```


```{r}
calculate_pct_diff <- function(data) {
  
  data %>% 
    mutate(sales_lag_1 = lag(sales, n = 1)) %>%
    mutate(sales_lag_1 = case_when(
      is.na(sales_lag_1) ~ sales,
      TRUE ~ sales_lag_1
    )) %>%
    mutate(diff_1 = sales - sales_lag_1) %>%
    mutate(pct_diff_1 = diff_1 / sales_lag_1) %>%
    mutate(pct_diff_1_chr = scales::percent(pct_diff_1))
}

bike_sales_m_tbl %>%
  calculate_pct_diff()
```


#3-2.Difference from first observation
```{r}
bike_sales_y_tbl %>%
  mutate(sales_2011 = first(sales)) %>%
  mutate(diff_2011  = sales - sales_2011) %>%
  mutate(pct_diff_2011 = diff_2011 / sales_2011) %>%
  mutate(pct_diff_2011_chr = scales::percent(pct_diff_2011))

bike_sales_m_tbl %>%
  
  group_by(year) %>%
  
  mutate(sales_jan = first(sales)) %>% 
  mutate(
    diff_jan         = sales - sales_jan,
    pct_diff_jan     = diff_jan / sales_jan,
    pct_diff_jan_chr = scales::percent(pct_diff_jan)
  ) 
```


#4.Cumulative Calculations
```{r}
bike_sales_y_tbl %>%
  mutate(cumulative_sales = cumsum(sales)) %>%
  mutate(cumulative_sales_pct = cumulative_sales / sum(sales)) %>%
  mutate(cumulative_sales_pct_chr = cumulative_sales_pct %>% scales::percent())

bike_sales_m_tbl %>%
  
  group_by(year) %>%
  
  mutate(cumulative_sales = cumsum(sales)) %>%
  mutate(cumulative_sales_pct = cumulative_sales / sum(sales)) %>%
  mutate(cumulative_sales_pct_chr = scales::percent(cumulative_sales_pct))
```


#5.Rolling Calculations
```{r}
bike_sales_m_tbl %>%
  
  mutate(roll_mean_3 = rollmean(sales, k = 3, na.pad = TRUE, align = "right", fill = NA)) %>%
  
  mutate(roll_mean_6 = rollmean(sales, k = 6, na.pad = TRUE, align = "right", fill = NA))

```


#6.Filtering Date Ranges 
```{r}
bike_orderlines_tbl %>%
  
  mutate(order_date = ymd(order_date)) %>%
  
  filter(order_date %>% between(left = ymd("2012-01-01"), right = ymd("2013-12-31"))) 

bike_orderlines_tbl %>%
  
  mutate(order_date = ymd(order_date)) %>%
  
  filter(year(order_date) %in% c(2012, 2013))
```


##data_wrangling_twse：

```{r}
library(tidyquant)
```


```{r}
tej <- read_tsv("D:/gitest/gitest01/0520/w2_importing data/tej_day_price_2017_2018_UTF8.txt", col_names = TRUE)
saveRDS(tej, "D:/gitest/gitest01/0520/w2_importing data/tej_d_2017_18.rds")
tej <- readRDS("D:/gitest/gitest01/0520/w2_importing data/tej_d_2017_18.rds")
```


#1.
```{r}
glimpse(tej)
tej1<-tej %>% select('證券代碼', '年月日', '收盤價(元)') %>% 
  rename(ID = '證券代碼', date = '年月日', close = '收盤價(元)') %>%      
  mutate(date = date %>% as.character %>% as.Date('%Y%m%d')) %>% 
  mutate(ID = ID %>% as.character) %>% 
  arrange(ID)  
tej1
```


#2.select 3 stocks from tej1: 1101, 2317, 2330
```{r}
tej.3 <- tej1 %>%
  arrange(ID) %>% 
  filter(ID %in% c("1101", "2317", "2330"))
tej.3
```


#3.

#選擇收盤價、選擇簡單移動平均線、5日簡單移動平均線參數。

#計算10日簡單移動平均線參數

#計算20日簡單移動平均線參數
```{r}
tej.3 <- tej.3 %>%
  group_by(ID) %>% 
  tq_mutate(select = c(close),  
            mutate_fun = SMA,           
            n = 5) %>%                
  rename(ma5 = SMA)  %>% 
  
  tq_mutate(select = c(close),
            mutate_fun = SMA,
            n = 10) %>%
  rename(ma10 = SMA) %>%
  
  tq_mutate(select = c(close),
            mutate_fun = SMA,
            n = 20) %>%
  rename(ma20 = SMA) %>% 
  ungroup()
tej.3        
```


#spread() long to wide
```{r}
tej.3 %>% select(-starts_with("ma")) %>% 
  spread(key = ID, value = close)
```

