---
title: "hw13"
author: "張瑜君"
date: "2019年5月27日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##checkpoint_3_forcats：
```{r}
library(tidyverse)
library(tidyquant)

bike_orderlines_tbl <- read_rds("data_wrangled_student/bike_orderlines.rds")

bike_orderlines_tbl
```


#1.Factor Basics 

#2.Motivating Example

#Manipulation
```{r}
sales_by_cat_2_tbl <- bike_orderlines_tbl %>%
    
    select(category_2, total_price) %>%
    
    group_by(category_2) %>%
    summarize(sales = sum(total_price)) %>%
    ungroup() %>%
    
    arrange(desc(sales)) %>%
    
    mutate(category_2 = category_2 %>% as_factor() %>% fct_rev())
```


#Plotting
```{r}
sales_by_cat_2_tbl %>%
    ggplot(aes(x = sales, y = category_2)) +
    geom_point(size = 5, color = "#2c3e50") +
    labs(title = "Sales By Category 2") +
    scale_x_continuous(labels = scales::dollar_format()) +
    theme_tq() +
    expand_limits(x = 0)

plot_sales <- function(data) {
    data %>%
        ggplot(aes(x = sales, y = category_2)) +
        geom_point(size = 5, color = "#2c3e50") +
        labs(title = "Sales By Category 2") +
        scale_x_continuous(labels = scales::dollar_format()) +
        theme_tq() +
        expand_limits(x = 0)
}

sales_by_cat_2_tbl %>%
    plot_sales()
```


#3.Forcats Basics

#3-1.Inspecting Factors

#Vector
```{r}
sales_by_cat_2_tbl %>% pull(category_2) %>% levels()

sales_by_cat_2_tbl %>% pull(category_2) %>% as.numeric()
```


#Tibble
```{r}
sales_by_cat_2_tbl %>%
    mutate(category_2 = category_2 %>% fct_rev() %>% fct_rev()) %>%
    mutate(
        label = category_2 %>% as.character(),
        value = category_2 %>% as.numeric()
    )
```


#3-2.Creating Factors: as_factor( ) vs as.factor( )
```{r}
sales_by_cat_2_tbl %>%
    mutate(
        category_2           = as.character(category_2),
        category_2_as_factor = as_factor(category_2) %>% as.numeric(),
        category_2_as.factor = as.factor(category_2) %>% as.numeric()
    )
```


#3-3.Reordering Factors: fct_reorder( ) and fct_rev( )
```{r}
sales_by_cat_2_tbl %>%
    arrange(desc(sales)) %>%
    mutate(sales_negative = -sales) %>%
    mutate(
        category_2 = category_2 %>% fct_reorder(sales_negative),
        values     = category_2 %>% as.numeric()) %>%
    
    plot_sales()
```


#3-4.Time-Based Reordering: fct_reorder2( ) 
```{r}
sales_by_cat_2_q_tbl <- bike_orderlines_tbl %>%
    
    mutate(order_date = order_date %>% floor_date("quarter") %>% ymd()) %>%
    
    group_by(category_2, order_date) %>%
    summarise(sales = sum(total_price)) %>%
    ungroup()

sales_by_cat_2_q_tbl


sales_by_cat_2_q_tbl %>%
    
    mutate(category_2 = category_2 %>% fct_reorder2(order_date, sales)) %>%
    
    ggplot(aes(x = order_date, y = sales, color = category_2)) +
    geom_point() +
    geom_line() +
    facet_wrap(~ category_2) +
    
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M"))
```


#3-5.Creating "Other" Category - fct_lump( ) & fct_relevel( ) 
```{r}
sales_by_cat_2_tbl %>%
    
    mutate(category_2 = category_2 %>% fct_lump(n = 6, 
                                                w = sales, 
                                                other_level = "All Other Bike Categories")) %>%
    
    group_by(category_2) %>%
    summarize(sales = sum(sales)) %>%
    
    mutate(category_2 = category_2 %>% fct_relevel("All Other Bike Categories", after = 0)) %>%
    
    plot_sales()
```


##02_ggplot2_geometries_1：
```{r}
library(tidyverse)
library(lubridate)
library(tidyquant)

bike_orderlines_tbl <- read_rds("data_wrangled_student/bike_orderlines.rds")

glimpse(bike_orderlines_tbl)
```


#1.Point / Scatter Plots

#Goal：Explain relationship between order value and quantity of bikes sold

#Data Manipulation
```{r}
order_value_tbl <- bike_orderlines_tbl %>%
    
    select(order_id, order_line, total_price, quantity) %>%
    
    group_by(order_id) %>%
    summarize(
        total_quantity = sum(quantity),
        total_price    = sum(total_price)
    ) %>%
    ungroup()
```


#Scatter Plot
```{r}
order_value_tbl %>%
    
    ggplot(aes(x = total_quantity, y = total_price)) +
    
    geom_point(alpha = 0.5, size = 2) +
    geom_smooth(method = "lm", se = FALSE)
```


#2.Line Plots

#Goal：Describe revenue by Month, expose cyclic nature

#Data Manipulation
```{r}
revenue_by_month_tbl <- bike_orderlines_tbl %>%
    
    select(order_date, total_price) %>%
    
    mutate(year_month = floor_date(order_date, "months") %>% ymd()) %>%
    
    group_by(year_month) %>%
    summarize(revenue = sum(total_price)) %>%
    ungroup()
```


#Line Plot
```{r}
revenue_by_month_tbl %>%
    
    ggplot(aes(year_month, revenue)) +
    
    geom_line(size = 0.5, linetype = 1) +
    geom_smooth(method = "loess", span = 0.2)
```


#3.Bar / Column Plots

#Goal：Sales by Descriptive Category

#Data Manipulation
```{r}
revenue_by_category_2_tbl <- bike_orderlines_tbl %>%
    
    select(category_2, total_price) %>%
    
    group_by(category_2) %>%
    summarize(revenue = sum(total_price)) %>%
    ungroup()
```


#Bar Plot
```{r}
revenue_by_category_2_tbl %>%
    
    mutate(category_2 = category_2 %>% as_factor() %>% fct_reorder(revenue)) %>%
    
    ggplot(aes(category_2, revenue)) +
    
    geom_col(fill = "#2c3e50") + 
    coord_flip()

```


#4.Histogram / Density Plots

#Goal：Unit price of bicycles

#Histogram
```{r}
bike_orderlines_tbl %>%
    
    distinct(model, price) %>%
    
    ggplot(aes(price)) +
    
    geom_histogram(bins = 25, fill = "blue", color = "white")
```


#Goal：Unit price of bicylce, segmenting by frame material

#Histogram
```{r}
bike_orderlines_tbl %>%
    
    distinct(price, model, frame_material) %>%
    
    ggplot(aes(price, fill = frame_material)) +
    
    geom_histogram() +
    
    facet_wrap(~ frame_material, ncol = 1) +
    
    scale_fill_tq() +
    theme_tq()
```


#Density
```{r}
bike_orderlines_tbl %>%
    
    distinct(price, model, frame_material) %>%
    
    ggplot(aes(price, fill = frame_material)) +
    
    geom_density(alpha = 0.5) +
    # facet_wrap(~ frame_material, ncol = 1) +
    
    scale_fill_tq() +
    theme_tq() +
    theme(legend.position = "bottom")
```


#5.Box Plot / Violin Plot

#Goal：Unit price of model, segmenting by category 2

#Data Manipulation
```{r}
unit_price_by_cat_2_tbl <- bike_orderlines_tbl %>%
    
    select(category_2, model, price) %>%
    distinct() %>%
    
    mutate(category_2 = as_factor(category_2) %>% fct_reorder(price))
```


#Box Plot
```{r}
unit_price_by_cat_2_tbl %>%
    
    ggplot(aes(category_2, price)) +
    
    geom_boxplot() +
    coord_flip() +
    theme_tq()
```


#Violin Plot & Jitter Plot
```{r}
unit_price_by_cat_2_tbl %>%
    
    ggplot(aes(category_2, price)) +
    
    geom_jitter(width = 0.15, color = "#2c3e50") +
    geom_violin(alpha = 0.5) +
    
    coord_flip() +
    theme_tq()
```


#6.Adding Text & Labels

#Goal：Exposing sales over time, highlighting outlier

#Data Manipulation
```{r}
revenue_by_year_tbl <- bike_orderlines_tbl %>%
    
    select(order_date, total_price) %>%
    
    mutate(year = year(order_date)) %>%
    
    group_by(year) %>%
    summarize(revenue = sum(total_price)) %>%
    ungroup()
```


#Adding text to bar chart

#Filtering labels to highlight a point
```{r}
revenue_by_year_tbl %>%
    
    # mutate(revenue_text = scales::dollar(revenue, scale = 1e-6, suffix = "M")) %>%
    
    ggplot(aes(year, revenue)) +
    
    geom_col(fill = "#2c3e50") +
    geom_smooth(method = "lm", se = FALSE) +
    
    geom_text(aes(label =  scales::dollar(revenue, scale = 1e-6, suffix = "M")), 
              vjust = 1.5, color = "white") +
    
    geom_label(label =  "Major Demand This Year",
               vjust = -0.5, 
               size  = 5,
               fill  = "#1f78b4",
               color = "white",
               fontface = "italic",
               data = revenue_by_year_tbl %>%
                   filter(year %in% c(2013))) + 
    
    expand_limits(y = 2e7) +
    theme_tq()
```

