---
title: "hw14"
author: "張瑜君"
date: "2019年6月3日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##02_iteration_and_scaling_functions_1：
```{r}
library(readxl)
library(tidyverse)
library(tidyquant)
library(lubridate)
library(broom)

bike_orderlines_tbl <- read_rds("data_wrangled_student/bike_orderlines.rds")

glimpse(bike_orderlines_tbl)
```


#1.PRIMER ON PURRR
#Programmatically getting Excel files into R
```{r}
excel_paths_tbl <- fs::dir_info("data/bike_sales/")

paths_chr <- excel_paths_tbl %>%
    pull(path)
```


#What Not To Do: Don't use for loops
```{r}
excel_list <- list()
for (path in paths_chr) {
    excel_list[[path]] <- read_excel(path)
}
excel_list
```


#Method 1: function name
```{r}
excel_list_2 <- paths_chr %>%
    map(read_excel) %>%
    set_names(paths_chr)
```


#Method 2: Anonymous Function
```{r}
paths_chr %>%
    map(~ read_excel(.))
```


#Method 3: Function specified with function()
```{r}
paths_chr %>%
    map(function(x) read_excel(path = x))
```


#Reading Excel Sheets
```{r}
excel_sheets("data/bike_sales/bikes.xlsx") %>%
    map(~ read_excel(path = "data/bike_sales/bikes.xlsx", sheet = .))
```


#2.MAPPING DATA FRAMES

#2-1.Column-wise Map
```{r}
bike_orderlines_tbl %>% is.list()

bike_orderlines_tbl %>%
    map(~ class(.))
```


#Character map
```{r}
bike_orderlines_tbl %>%
    map_chr(~ class(.)[1])
```


#Data Frame map
```{r}
bike_orderlines_tbl %>%
    map_df(~ class(.)[1]) %>%
    gather()

bike_orderlines_tbl %>%
    map_df(~ sum(is.na(.)) / length(.)) %>%
    gather()
```


#2-3.Row-wise Map
```{r}
excel_tbl <- excel_paths_tbl %>%
    select(path) %>%
    mutate(data = path %>% map(read_excel))

excel_list

excel_tbl
```


#3.NESTED DATA

#Unnest
```{r}
excel_tbl

excel_tbl$data

excel_tbl$data[[3]]

excel_tbl_unnested <- excel_tbl %>%
    unnest(data, .id = 'ID') 

excel_tbl_unnested
```


#Nest
```{r}
excel_tbl_nested <- excel_tbl_unnested %>%
    group_by(ID, path) %>%
    nest()

excel_tbl_nested$data
```


#Mapping Nested List Columns
```{r}
x <- rep(NA, 5)
x

!is.na(x) %>% all()

y <- c(1:4, NA_real_)
y

!is.na(y) %>% all()

all(!is.na(y))

excel_tbl_nested$data[[1]] %>%
    select_if(~ !is.na(.) %>% all())

excel_tbl_nested
```


#Method 1: Creating a function outside of purrr::map()

#Step 1: Create a function that can be mapped to one element 
```{r}
select_non_na_columns <- function(data) {
    
    data %>%
        select_if(~ !is.na(.) %>% all())
    
}
```


#Step 2: Extract an element, and test the function
```{r}
excel_tbl_nested$data[[1]] %>%
    select_non_na_columns()
```


#Step 3: Use mutate() + map()
```{r}
excel_tbl_nested_fixed <- excel_tbl_nested %>%
    mutate(data_fixed = data %>% map(select_non_na_columns))

excel_tbl_nested_fixed$data[[1]]
```


#4.MODELING WITH PURRR

#4-1.Time Series Plot

#What if we wanted to approximate the 3 month rolling average with a line?

#We can use a smoother

#Code comes from 04_functions_iteration/01_functional_programming
```{r}
rolling_avg_3_tbl <- bike_orderlines_tbl %>%
    select(order_date, category_1, category_2, total_price) %>%
    
    mutate(order_date = ymd(order_date)) %>%
    mutate(month_end = ceiling_date(order_date, unit = "month") - period(1, unit = "days")) %>%
    
    group_by(category_1, category_2, month_end) %>%
    summarise(
        total_price = sum(total_price)
    ) %>%
    mutate(rolling_avg_3 = rollmean(total_price, k = 3, fill = NA, align = 'right')) %>%
    ungroup() %>%
    
    mutate(category_2 = as_factor(category_2) %>% fct_reorder2(month_end, total_price)) 

rolling_avg_3_tbl %>%
    
    ggplot(aes(month_end, total_price, color = category_2)) +
    
    
    geom_point() +
    geom_line(aes(y = rolling_avg_3), color = "blue", linetype = 1) +
    facet_wrap(~ category_2, scales = "free_y") +
    
  
    geom_smooth(method = "loess", se = FALSE, span = 0.2, color = "black") +

    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar_format(scale = 1e-3, suffix = "K"))
```


#4-2.Modeling Primer

#Data Preparation
```{r}
sales_by_m_cross_country_tbl <- rolling_avg_3_tbl %>%
    
    filter(category_2 == "Cross Country Race") %>%
    
    select(month_end, total_price) %>%
    
    mutate(month_end_num = as.numeric(month_end))


sales_by_m_cross_country_tbl %>%
    
    ggplot(aes(month_end_num, total_price)) +
    geom_point() +
    geom_smooth(method = "loess", span = 0.2, se = FALSE)
```


#Making a loess model
```{r}
fit_loess_cross_country <- sales_by_m_cross_country_tbl %>%
    
    loess(total_price ~ month_end_num, data = ., span = 0.2)

fit_loess_cross_country
```


#Working With Broom
```{r}
fit_loess_cross_country %>%
    broom::augment() %>%
    
    
    # Visualizing results
    ggplot(aes(month_end_num, total_price)) +
    geom_point() +
    geom_line(aes(y = .fitted), color = "blue")
```


#4-3.Step 1: Function To Return Fitted Results
```{r}
rolling_avg_3_tbl_nested <- rolling_avg_3_tbl %>%
    group_by(category_1, category_2) %>%
    nest()

rolling_avg_3_tbl_nested$data[[1]]


data <- rolling_avg_3_tbl_nested$data[[1]]

tidy_loess <- function(data, span = 0.2) {
    
    data_formatted <- data %>%
        select(month_end, total_price) %>%
        mutate(month_end_num = as.numeric(month_end))
    
    fit_loess <- loess(formula = total_price ~ month_end_num, 
                       data    = data_formatted, 
                       span    = span)
    
    output_tbl <- fit_loess %>%
        broom::augment() %>%
        select(.fitted)
    
    return(output_tbl)
    
}
```


#4-4.Step 2: Test Function on Single Element ----
```{r}
rolling_avg_3_tbl_nested$data[[2]] %>%
    tidy_loess()
```


#4-5.Step 3: Map Function to All Categories ----

#Map Functions
```{r}
loess_tbl_nested <- rolling_avg_3_tbl_nested %>%
    mutate(fitted = data %>% map(tidy_loess))

loess_tbl_nested$fitted[[1]]

loess_tbl_nested %>%
    unnest()
```


#Visualize Results
```{r}
loess_tbl_nested %>%
    
    unnest() %>%
    
    ggplot(aes(month_end, total_price, color = category_2)) +
    
    geom_point() +
    geom_line(aes(y = .fitted), color = "blue", size = 2) +
    geom_smooth(method = "loess", span = 0.2) +
    facet_wrap(~ category_2, scales = "free_y") 
```








